### 2013-09-17 manuscripts/reply/reply.tex
More work on reply.

\citet{Oaks2012} suggest that more cogent prior probability distributions on
divergence models and nuisance parameters could mitigate the effect of
Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in prior selection, and champion the method
as a means of avoiding the pitfalls raised by \citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.
The approach merely provides another means by which the model can ``escape''
large parameter space, and the bias towards models with smaller space still
remaines.

@@

\bibliography{../bib/references}

@@

%:FIGURE-accuracy omega SS GLM
\begin{figure}[hbtp]
    \captionsetup{listformat=figList}
    \centering
    \includegraphics[width=1.0\textwidth]{../../saturation/saturation-plot.pdf}
    \caption{
        Saturation plot \ldots
    }
    \label{fig_saturation_plot}
\end{figure}

>>>>

\citet{Oaks2012} suggest that more cogent prior probability distributions on
divergence models and nuisance parameters could mitigate the effect of
Lindley's paradox.
They also layout a set of simulation-based procedures for determining power,
accuracy, and robustness of the method given a dataset, and recommend any
application of \msb should be accompanied by such procedures, especially
if any biological conclusions are going to drawn from the results.
\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
for accommodating uncertainty in selecting among empirically guided priors, and
champion the method as a means of avoiding the pitfalls raised by
\citet{Oaks2012}.
Unfortunately, we show that fundamental errors in this approach render some of
their results invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s \citeyear{Hickerson2013}
approach.
Our results demonstrate that the method is biased and dangerous.
The approach merely provides another means by which the model can ``escape''
large parameter space, and the bias towards models with smaller space still
remains.
This bias can be dangerous and often excludes the true parameter space due to
the use of uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.

\section*{Their power analysis}
\citet{Hickerson2013} present a power analysis in which they demonstrate that
\msb has the power to infer multiple divergence events when divergence times
are random over hundreds of thousands of generations (rather than millions
as demonstrated by \citet{Oaks2012}.
It is not surprising to find that within certain parameter space the method
has increased power to detect temporal variation in divergences over narrower
time windows than millions of generations.
However, what is important to consider is whether those conditions are relevant
to real world applications of the method.
\citet{Oaks2012} explore the behavior of the method under three divergence time
priors as narrow as 0--5 coalescent units, which is quite narrow considering
that this expresses the prior belief that all 22 taxon pairs diverged within
this window.
\citet{Hickerson2013} limit their power analysis to a single prior of 0--1
coalescent unit.
It seems that being 100\% certain a priori that all taxa under comparison
diverged within the last coalescent unit is not generally applicable to most
empirical systems.
Furthermore, even when such extensive prior information is available to only be
able to detect multiple divergences on the scale of hundreds of thousands of
generations does not seem very ``powerful.''

Also, \citet{Hickerson2013} present information only on the extreme case of a
single divergence event.
As discussed in \citet{Oaks2012}, it seems dubious to consider the estimation
of two divergence events as a success when divergence is random over hundreds
of thousands of generations.
Unlike the results of \citet{Oaks2012} it is impossible to assess the
performance of \msb based on the results presented by \cite{Hickerson2013}
other than to know whether or not it inferred the worst possible scenario of a
single event.
In an empirical system such as the Philippines, where island fragmentation
has occurred at least X times over the past several millions of years, an
estimate where 22 taxa share even a handful of divergence events would be
of biogeographic interest.
\citet{Hickerson2013} seem to suggest in their response that \msb should only
be used as a binary estimator; i.e., was there one event or more?
This is not consistent with how \msb has been presented, used, and interpreted
in the past.

\section*{Differing utilities of \numt{} and \vmratio{} in \msb}
We preface this section with a clarification of an issue that has
been confused throughout the \msb literature.
The mean (\meant{}), variance (\vart{}), and dispersion index
($\vart{}/\meant{} = \vmratio{}$) of divergence times are \emph{not} parameters
of the model implemented in \msb.
Rather they are statistics that summarize parameters of the model.
This is in contrast to \numt{}, which is a parameter of the model.

\citet{Hickerson2013} strongly argue that \vmratio{} is a better estimator than
\numt{}, but the logic behind the argument is dubious.
They present a plot of \numt{} against \vmratio{} (Fig.~S1) which is simply a
plot of sample size versus variance.
After showing that \vmratio{} has essentially no information about the
number of divergences, they conclude it is more informative and biogeographically
relevant.
We struggle to follow this logic.
Certainly the maximum information is contained within the divergence time
vector that \vmratio{} is summarizing.
The temporal information contained in this vector coupled with its cardinality
(\numt{}) is certainly more informative than its summary.
The dispersion index is not a sufficient statistic for this vector.

They also argue that ``\msb can estimate \vmratio{} much better than \numt{}.''
However, the primary objective of \msb is to estimate the posterior probability
of divergence models.
\citet{Oaks2012} demonstrate that even when all assumptions of the model are
met, \vmratio is a terrible model-choice estimator (see plots B, D \& F of
Figure 4), whereas \numt{} performs better.
Furthermore, \vmratio{} is limited to estimating the probability of only a
single divergence model (the one divergence model), and thus its utility for
model choice is extremely limited.

@@

% \bibliography{../bib/references}
\bibliography{references}

@@

%:FIGURE-saturation plot
\mFigure{../../saturation/saturation-plot.pdf}{
    Saturation plot \ldots
}{figSaturationPlot}

\mFigure{../../response-redux/results/hickerson/pymsbayes-results/mean_by_dispersion.pdf}{
    Results of reanalysis.
}{figJointPosterior}

\mFigure{../../response-redux/results/sampling-error/pymsbayes-results/omega_over_sampling.pdf}{
    Sampling error \ldots
}{figSamplingError}

%% Exclusion simulation results
\mFigure{../../model-choice/results/m1-1-sim/pymsbayes-results/num_tau_excluded.pdf}{
    Histogram of the number of \divt{} parameters excluded.
}{figExclusionSimTau}

\mFigure{../../model-choice/results/m1-1-sim/pymsbayes-results/prob_of_exclusion.pdf}{
    Histogram of the posterior probability of excluding the truth.
}{figExclusionSimProb}

%% Power results
\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_accuracy_omega_median.pdf}{
    Histograms of the posterior probability that $\vmratio{} < 0.01$.
}{figPowerAccOmegaMedian}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_accuracy_omega_mode_glm.pdf}{
    Histograms of the posterior probability that $\vmratio{} < 0.01$.
}{figPowerAccOmegaModeGLM}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_psi_mode.pdf}{
    Histograms of \numt{} estimates.
}{figPowerPsiMode}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_omega_prob.pdf}{
    Histograms of the posterior probability that $\vmratio{} < 0.01$.
}{figPowerOmegaProb}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_prob_exclusion.pdf}{
    Histograms of the posterior probability of excluding the truth.
}{figPowerProbExclusion}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_num_excluded.pdf}{
    Histograms of the number of true \divt{} parameters excluded.
}{figPowerNumExcluded}

%% Validation results
\mFigure{../../model-choice/results/validation/results/pymsbayes-results/plots/mc_behavior.pdf}{
    True versus estimated probability of a single divergence event.
}{figValidationMCBehvior}
